---
output: word_document
---
====================================================================

# Inferencial Data Analysis

====================================================================

## 1. Load the ToothGrowth data and perform some basic exploratory data analyses 

Load and see the data
```{r, echo=TRUE}
library(datasets)
data = ToothGrowth
str(data)
```

Basic Exploratory Data Analysis of the data
```{r, echo=TRUE}
require(graphics)
plot1 = coplot(len ~ dose | supp, data = ToothGrowth, panel = panel.smooth,
       xlab = "ToothGrowth data: length vs dose, supplement type")
```

## 2. Basic Assumptions

1. Poplulations are independent, that the variances between populations are different, a random population was used. 

2. The population was comprised of similar guinea pigs, measurement error was accounted for.

## 3. Null hypothesis & Confidence Interval

### Supplement as a factor

Assumption: Null Hypothesis says that there is no corellation between toothgrowth and supplement and therefore the difference in mean of toothgrowth between two supplements is zero.

Lets test the null hypothesis
```{r, echo=TRUE}
t.test(len ~ supp, paired = F, var.equal = F, data = ToothGrowth)
```

Conclusion: A confidence interval of [-0.171, 7.571] does not allow us to reject the null hypothesis. Therefore our hypothesis that there is no correlation between delivery method and tooth length is strong.

### Dosage as a factor

Assumption: Null Hypothesis says that there is no corellation between toothgrowth and dosage and therefore the difference in mean of toothgrowth on different dosages is zero.

To test dosage as a foactor, we test the toothgrowth data between different dosages.
```{r,echo=TRUE}
dose1 <- subset(ToothGrowth, dose %in% c(0.5, 1.0))
dose2 <- subset(ToothGrowth, dose %in% c(0.5, 2.0))
dose3 <- subset(ToothGrowth, dose %in% c(1.0, 2.0))
```

First we test between dosage 0.5 & 1
```{r,echo=TRUE}
t.test(len ~ dose, paired = F, var.equal = F, data = dose1)
```

Between dosage 0.5 & 2
```{r, echo = TRUE}
t.test(len ~ dose, paired = F, var.equal = F, data = dose2)
```

Between dosage 1 & 2
```{r, echo=TRUE}
t.test(len ~ dose, paired = F, var.equal = F, data = dose3)
```

Conclusions: The confidence intervals ([-11.98, -6.276] for doses 0.5 and 1.0, [-18.16, -12.83] for doses 0.5 and 2.0, and [-8.996, -3.734] for doses 1.0 and 2.0) allow for the rejection of the null hypothesis. 

Hence we reject the null hypothesis that there is no relation between diferrent dosages. 

Infact there is a strong corellation netween dosage and toothgrowth.